Atomic Investigation on Cold Deformation Behavior of Two Phase TiAl Polycrystal with and without Void Defect

### 2018-11-10 draft/alexpub.tex
change figure

\section{Introduction}
% and brittle rapture failure 
Poor Ductility at room temperature in Ti-Al alloy strongly affects the safety of fracture of structure like turbo of aircraft engine and combustion generator \cite{Munz2017}. Deformation phenomena of TiAl alloys have been widely studied in order to overcome the problems associated with the limited ductility and damage tolerance.  Much of the work has been performed on single phase $\gamma$ alloys and PST crystals\cite{Appel2016}. Rapture failure at the macroscopic scale can be attributed to nucleation, growth and propagation of cracks, but at the microscopic scale cracks are initially easily formed at defects in the casting process, such as voids and inclusions \cite{Tang2014}.

@@

where the prefactor $v_0$ gives the velocity that would be obtained for each potential mobility, $L$ is the free length of screw character of dislocation, $\Delta H(\tau^*)$ is activation enthalpy determined by loading conditions. The effect of temperature on the mobility can be obtained under different loading conditions, we chose  $$\Delta H(\tau_1^*) > \Delta H(\tau_2^*) > \Delta H(\tau_3^*)$$, thus  $\Delta H(\tau^*)$ are different. We choose cases with different loading condition$\Delta H(\tau^*)$  , normalized velocity can be  case 1 to case 3  in a increase order of $\Delta H(\tau^*)$.

\begin{figure}[ht]
	\centering
	\begin{minipage}{0.495\textwidth}
		\includegraphics[width=1\linewidth]{img/temp}
		\centering
		\caption{Mobility of dislocation\\
		}
		\label{fig:temp}
	\end{minipage}	
	\hfill
	\begin{minipage}{0.495\textwidth}		
		\includegraphics[width=1\linewidth]{img/disum}
		\centering
		\caption{Strength of models}
		\label{fig:disum}
	\end{minipage}
\end{figure}

@@

Void of R=10 \AA\ was placed at phase boundary, inside $\alpha_2$ phase grain respectively. Effect of void at different position under uniaxial tension is shown in Fig.\ref{fig:stress&strain}. The strength of materials with void in different size and at different position is shown in Fig.\ref{fig:stress&strain}. The results show that the model without void defect has best strength, while the void located inside $\alpha_2$ phase detracts the strength of the material most, and the void at phase boundary have less impact on the strength.

@@

where $\sigma_0$ is the strength of the model without void defects 5.26 Gpa, and $A_0$ is initial section area, $ A = 36000 {AA}^2$, $A^* $ is section area in consider of the subsection that results from the voids. Comparing with the strength determined by molecular dynamics simulation and the results calculated with formulation \ref{eq:section}, it can be assumed that the main factor that affects the strength of materials can be attributed to local behavior of the materials, thus revolution of defects should be examined carefully.

>>>>

\section{Introduction}
% and brittle rapture failure 
Poor Ductility at room temperature in Ti-Al alloy strongly affects the safety of fracture of structures like turbo of aircraft engine and combustion generator \cite{Munz2017}. Deformation phenomena of TiAl alloys have been widely studied in order to overcome the problems associated with the limited ductility and damage tolerance.  Much of the work has been performed on single phase $\gamma$ alloys and PST crystals\cite{Appel2016}. Rapture failure at the macroscopic scale can be attributed to nucleation, growth and propagation of cracks, but at the microscopic scale cracks are initially easily formed at defects in the casting process, such as voids and inclusions \cite{Tang2014}.

@@

where the prefactor $v_0$ gives the velocity that would be obtained for each potential mobility, $L$ is the free length of screw character of dislocation, $\Delta H(\tau^*)$ is activation enthalpy determined by loading conditions. The effect of temperature on the mobility can be evaluated under different loading conditions, thus we chose  $\Delta H(\tau_1^*) > \Delta H(\tau_2^*) > \Delta H(\tau_3^*)$ in formula \ref{eq:temp-dis}, normalized velocity is shown in fig \ref{fig:temp}. The relative velocity  of dislocation rise along with increase of  stress, the speed of dislocation

\begin{figure}[ht]
	\centering
	\begin{minipage}{0.495\textwidth}
		\includegraphics[width=1\linewidth]{img/temp}
		\centering
		\caption{Mobility of dislocation}
		\label{fig:temp}
	\end{minipage}	
	\hfill
	\begin{minipage}{0.495\textwidth}		
		\includegraphics[width=1\linewidth]{img/disum}
		\centering
		\caption{Dislocation length during different stages}
		\label{fig:disum}
	\end{minipage}
\end{figure}

@@

Void with different sizes was placed at $\alpha_2-\gamma$ phase boundary, inside $\gamma$ phase respectively. Effect of void on the strength at different position under uniaxial tension is shown in Fig.\ref{fig:stress&strain}. The strength of materials with void in different size and at different position is shown in Fig.\ref{fig:stress&strain}. The existence of void have little impact on the elastic properties of the material, and the model without void defect has best strength 5.3 GPa, the yield stress of model with void is smaller. located inside $\alpha_2$ phase detracts the strength of the material most, and the void at phase boundary have less impact on the strength.

@@

where $\sigma_0$ is the strength of the model without void defects 5.26 Gpa, and $A_0$ is initial section area, $ A = 36000 {AA}^2$, $A^* $ is section area in consider of the subsection that results from the voids. Comparing with the strength determined by molecular dynamics simulation and the result4s calculated with formulation \ref{eq:section}, it can be assumed that the main factor that affects the strength of materials can be attributed to local behavior of the materials, thus revolution of defects should be examined carefully.
